>

### 2019-05-15 paper/spinifex-paper.tex
Structure, wording, and notaion

\begin{itemize}
\tightlist
\item
  \(\textbf{X}\), the data, an \(n \times p\) numeric matrix to be
  projected to 2D.
\item
  \(\textbf{B} = (B_1,~ B_2)\), any 2D orthonormal projection basis,
  \(p \times 2\) matrix, describing the projection from \(p\) to two
  dimensions. We will call this the ``original projection'' because it
  is the starting point for the manual tour.
\item
  \(k\), is the index of the variable to manipulate, called the ``manip
  var''.
\item
  \(|\textbf{B}_k|\), the norm of the manip var, \(k\), the length of
  this basis vector between 0 and 1 inclusive.
\item
  \(\textbf{e}\), a 1D coordinate basis vector of length \(p\) with the
  \(k\)-th element set to one and orthonormalized on the end of
  \(\textbf{B}\).
\item
  \(\theta\), the angle of in-projection-plane rotation, for example, on
  the reference axes; \(c_\theta, s_\theta\) are the cosine and sine.
\item
  \(\phi\), the angle of out-of-projection-plane rotation, into the
  manipulation space; \(c_\phi, s_\phi\) are the cosine and sine.
\item
  \(\textbf{U}\) is the axis of rotation for \(\phi\).
\end{itemize}

@@

An initial 2D projection basis set must be provided. One way to identify
a projection containing interesting features is to apply a guided tour.
In a guided tour, the projection sequence is selected by optimizing an
index function via hill-climbing on the projection space. In this case,
the holes index is selected and applied to the standardized flea data.
The holes index is maximized when the projected observations are
furthest from the center. Figure \ref{fig:step0} shows a locally
optimized projection of the data. The left panel displays the reference
axes of the projection basis, a visual indication of the magnitude and
direction each variable contributes to the projection. The right panel
shows the data as projected through the basis set described by the
reference axes (left). Data points are colored and given shape according
to the species.

Call \code{view\_basis()} on a basis to produce a \CRANpkg{ggplot2}
(Wickham \protect\hyperlink{ref-wickham_ggplot2:_2016}{2016}) graphic
similar to Figure \ref{fig:step0}. The projected data is processed for
display using matrix multiplication
\(\textbf{X}_{[n,~p]} ~*~ \textbf{B}_{[p,~d]} ~=~ \textbf{P}_{[n,~d]}\).

@@

Initialize the coordinate basis vector as a zero vector \(\textbf{e}\)
of length \(p\), and set the \(k\)-th element to 1. In the example data,
aede2 is the fifth variable in the data, so \(k=5\), set \(e_5=1\) . Use
a Gram-Schmidt process to orthonormalize the coordinate basis vector on
the original 2D projection to describe a 3D manipulation space,
\(\textbf{M}\).

@@

The manip space provides a 3D projection from \(p\)-dimensional space,
where the coefficient of the manip var can range completely between
{[}-1, 1{]}. 3D rotation can be used to rotate the mani variable
completely into or completely out of a 2D projection. Figure
\ref{fig:step2} illustrates this 3D manipulation space with the manip
var highlighted. This representation is produced by calling the
\code{view\_manip\_space()} function. Functionally, the manipulation
space is more of a mathematical construct that needn't be visualized but
this diagram provides intuition for the technique.

@@

For a radial tour fix the (horizontal) angle within the projection
plane, \(\theta\), and define a sequence for the (vertical) angle coming
out of the projection plane, \(\phi\), bringing the initial \(XY\)
contributions of the manip var to a maximum and then to zero before
returning to the initial position. Alternatively, for an oblique manual
tour, capture the user manipulation directly on the \(XY\) of the
projection plane.

@@

The steps outlined above can be used to create any arbitrary rotation in
the manip space. To use these for sensitivity analysis, the radial
rotation is built into an animation where the manip var is rotated fully
into the projection, completely out, and then back to the start. This
involves changing \(\phi\), the angle relative to its initial value.
Apply the transformation \(\phi_i \leftarrow \phi_i-\phi_1\). When
\(\phi\) is 0, the manip var is completely in the projection, and when
\(\phi\) is \(\pi/2\), \(\textbf{B}_k\) is not contributing at all.

@@

In each of the steps 3-5, a small step may be made to bring it exactly
to the end position.

@@

\caption[Radial manual tour manipulating aede2 of standardized flea data]{Radial manual tour manipulating aede2 of standardized flea data.  The contributions increase from its initial contribution to a full contribution to the projection before decreasing to zero and then returning to its initial value. Manipulating the coefficeients of aede2 changes the distance separating the purple cluster. This shows that aede2 is important for distinguishing this species from the ramaining data. Animated versions made with the \code{play\_manual\_tour()} function and can be viewed at https://nspyrison.netlify.com/thesis/flea\_manualtour\_mvar5/.}\label{fig:step4}
\end{figure}
\end{Schunk}

@@

The value of \(\phi\) is relative to its initial value. The
transformation \(\phi_i\) - \(\phi_1\) is useful to think about \(\phi\)
relative to the basis plane. Additionally, the value of \(\phi\) may be
out of phase by a factor of \(\pi\). If the manip variable doesn't move
as expected these are the first places to check.

\hypertarget{sec:display}{%
\subsection{Data in projection-space}\label{sec:display}}

@@

The primary functions that will aid users in performing their own manual
tours are broken into the following groupings: tour preparation, tour
animation, and utility.

@@

In the following section describes and demonstrates the usage of the
above functions following the order in the algorithm. The utility
functions are called by the tour animation functions, passed to the
argument \code{render\_type}. Usage is demonstrated below and in the
example documentation.

@@

Radial manual tours were applied to a dataset across different
experiments of hadronic collisions. The importance of selecting the
correct manip var, as demonstrated by comparing tours of varying amounts
of structural information. Manual tours, by giving the full contribution
of the manipulation space to the manip var, enable analysts to explore
the sensitivity of the structure with the selected variable. This
information can be used by domain experts to identify which variables
are probing which parameter spaces and how sensitive those variables are
to structural features. This insight can be indispensable for variable
inclusion/exclusions in a model, or in high-level decisions, such as
budgeting time and funding.

>>>>

\begin{itemize}
\tightlist
\item
  \(\textbf{X}\), the data, an \(n \times p\) numeric matrix to be
  projected to 2D.
\item
  \(\textbf{B} = (B_1,~ B_2)\), any 2D orthonormal projection basis,
  \(p \times 2\) matrix, describing the projection from \(p\) to two
  dimensions. We will call this the ``original projection'' because it
  is the starting point for the manual tour.
\item
  \(k\), is the index of the variable to manipulate, called the ``manip
  var''.
\item
  \(|\textbf{B}_k|\), the norm of the manip var, \(k\), the length of
  this basis vector between 0 and 1 inclusive.
\item
  \(\textbf{e}\), a 1D coordinate zero basis vector of length \(p\) with
  the \(k\)-th element set to one.
\item
  \(\textbf{M} = orthonormalize(\textbf{B}|\textbf{e})\), the
  manipulation space, a \(p \times 3\) matrix where out-of-plane
  rotation takes place.
\item
  \(\theta\), the angle of in-projection-plane rotation, for example, on
  the reference axes; \(c_\theta, s_\theta\) are the cosine and sine.
\item
  \(\phi\), the angle of out-of-projection-plane rotation, into the
  manipulation space; \(c_\phi, s_\phi\) are the cosine and sine.
\item
  \(\textbf{U}\), the axis of rotation for \(\phi\).
\item
  \(\textbf{R}\), the rotation matrix, containing the rotaions of
  \(\theta\) and \(\phi\) within the manipulation space, \(\textbf{M}\).
\item
  \(\textbf{RM} = \textbf{M} * \textbf{R}\), the result of the
  manipulation space after the application of the rotation matrix.
\item
  \(\textbf{P} = \textbf{X} * \textbf{RM}\), the data projection, the
  data as projected through the rotated manipulation space.
\end{itemize}

@@

An initial 2D projection basis set must be provided. One way to identify
a projection containing interesting features is to apply a guided tour.
In a guided tour, the projection sequence is selected by optimizing an
index function via hill-climbing on the projection space. In this case,
the holes index is selected and applied to the standardized flea data.
The holes index is maximized when the projected observations are
furthest from the center.

Figure \ref{fig:step0} shows a locally optimized projection of the data.
The left panel displays the reference axes of the projection basis, a
visual indication of the magnitude and direction each variable
contributes to the projection. The right panel shows the data as
projected through the basis set described by the reference axes (left).
Data points are colored and given shape according to the species. Call
\code{view\_basis()} on a basis to produce a \CRANpkg{ggplot2} (Wickham
\protect\hyperlink{ref-wickham_ggplot2:_2016}{2016}) object similar to
Figure \ref{fig:step0}. The projected data is processed for display
using matrix multiplication,
\(\textbf{P}_{[n,~d]} ~=~ \textbf{X}_{[n,~p]} ~*~ \textbf{B}_{[p,~d]}\).

@@

Initialize the coordinate basis vector as a zero vector \(\textbf{e}\)
of length \(p\), and set the \(k\)-th element to 1. In the example data,
aede2 is the fifth variable in the data, so \(k=5\), set \(e_5=1\). Use
a Gram-Schmidt process to orthonormalize the coordinate basis vector on
the original 2D projection to describe a 3D manipulation space,
\(\textbf{M}\).

@@

The manip space provides a 3D projection from \(p\)-dimensional space,
where the coefficient of the manip var can range completely between
{[}-1, 1{]}. 3D rotation can be used to rotate the manip variable
completely into or completely out of a 2D projection. Figure
\ref{fig:step2} illustrates this 3D manipulation space with the manip
var highlighted. This representation is produced by calling the
\code{view\_manip\_space()} function. Functionally, the manipulation
space adds another layer of complexity that needn't be displayed in the
final animation, but this diagram aids in comprehension of the
technique.

@@

For a radial tour fix the (horizontal) angle within the projection
plane, \(\theta\), and define a sequence for the (vertical) angle coming
out of the projection plane, \(\phi\), bringing the initial value of
\(|\textbf{B}_k|\) to a maximum and then to zero before returning to the
initial position. Alternatively, for an \emph{oblique} manual tour,
capture the user manipulation directly on the \(XY\) of the projection
plane.

@@

The steps outlined above can be used to create any arbitrary rotation in
the manip space. To use these for sensitivity analysis, the radial
rotation is built into an animation where the manip var is rotated fully
into the projection, completely out, and then back to the initial value.
This involves changing \(\phi\), the angle relative to its initial
value. Apply the transformation \(\phi_i \leftarrow \phi_i-\phi_1\) such
that \(\phi\) is relative to the projection plane. When \(\phi\) is 0,
\(|\textbf{B}_k| = 1\), and when \(\phi\) is \(\pi/2\), the manip var
has no contribution to the projection.

@@

In each of the steps 3-5, a small step may be appended to bring \(\phi\)
exactly to the desired value.

@@

\caption[Radial manual tour manipulating aede2 of standardized flea data]{Radial manual tour manipulating aede2 of standardized flea data. The contributions increase from its initial vlaue to a full contribution to the projection before decreasing to zero and then returning to the initial value. Manipulating the coefficeients of aede2 changes the distance separating the purple cluster. This shows that aede2 is important for distinguishing this species from the ramaining data. Animated versions made with the \code{play\_manual\_tour()} function and can be viewed at https://nspyrison.netlify.com/thesis/flea\_manualtour\_mvar5/.}\label{fig:step4}
\end{figure}
\end{Schunk}

@@

The value of \(\phi\) is relative to its initial value. The
transformation \(\phi_i\) - \(\phi_1\) is useful to think about \(\phi\)
relative to the basis plane. Additionally, the value of \(\phi\) may be
out of phase by a factor of \(\pi\). If the rotation does not behave as
expected these are the first places to check.

\hypertarget{sec:display}{%
\subsection{Projecting the data}\label{sec:display}}

@@

The primary functions that will aid users in performing their own manual
tours are broken into the following groupings: tour preparation, tour
animation, and utility. In the following section describes and
demonstrates the usage of the above functions following the order in the
algorithm. The utility functions are called by the tour animation
functions, passed to the argument \code{render\_type}. Usage is
demonstrated below and in the example documentation.

@@

@@

Radial manual tours were applied to a dataset across different
experiments of hadronic collisions. The importance of selecting the
correct manip var, as demonstrated by comparing tours of varying amounts
of structural information. Manual tours, by controlling the contribution
of the manip var on the projection, enable analysts to explore the
sensitivity that variable has on the structure of the projection. This
information can be used by domain experts to identify which variables
are probing which parameter spaces and how sensitive structural features
are to different variables. This insight can be indispensable for
variable inclusion/exclusion, and in higher-level decisions, such as
meta-analysis, to suggest directions of future research.

### 2019-05-15 paper/spinifex_paper.Rmd
Structure, wording, and notaion

- $\textbf{X}$, the data, an $n \times p$ numeric matrix to be projected to 2D.
- $\textbf{B} = (B_1,~ B_2)$, any 2D orthonormal projection basis, $p \times 2$ matrix, describing the projection from $p$ to two dimensions. We will call this the "original projection" because it is the starting point for the manual tour.
- $k$, is the index of the variable to manipulate, called the "manip var".
- $|\textbf{B}_k|$, the norm of the manip var, $k$, the length of this basis vector between 0 and 1 inclusive.
- $\textbf{e}$, a 1D coordinate basis vector of length $p$ with the $k$-th element set to one and orthonormalized on the end of $\textbf{B}$. 
- $\theta$, the angle of in-projection-plane rotation, for example, on the reference axes; $c_\theta, s_\theta$ are the cosine and sine.
- $\phi$, the angle of out-of-projection-plane rotation, into the manipulation space; $c_\phi, s_\phi$ are the cosine and sine.
- $\textbf{U}$ is the axis of rotation for $\phi$.

<!-- operate on bases -->
The algorithm operates entirely on projection bases and utilizes the data only later when making a display. <!--The projection space can be viewed at any point in the process by pre-multiplying the data and plotting the first two variables.-->

@@

<!-- Projection basis -->
An initial 2D projection basis set must be provided. One way to identify a projection containing interesting features is to apply a guided tour. In a guided tour, the projection sequence is selected by optimizing an index function via hill-climbing on the projection space. In this case, the holes index is selected and applied to the standardized flea data. The holes index is maximized when the projected observations are furthest from the center. Figure \ref{fig:step0} shows a locally optimized projection of the data. The left panel displays the reference axes of the projection basis, a visual indication of the magnitude and direction each variable contributes to the projection. The right panel shows the data as projected through the basis set described by the reference axes (left). Data points are colored and given shape according to the species.

Call \code{view\_basis()} on a basis to produce a \CRANpkg{ggplot2} [@wickham_ggplot2:_2016] graphic similar to Figure \ref{fig:step0}. The projected data is processed for display using matrix multiplication $\textbf{X}_{[n,~p]} ~*~ \textbf{B}_{[p,~d]} ~=~ \textbf{P}_{[n,~d]}$.

@@

<!-- Zero Vect, manip sp -->
Initialize the coordinate basis vector as a zero vector $\textbf{e}$ of length $p$, and set the $k$-th element to 1. In the example data, aede2 is the fifth variable in the data, so $k=5$, set $e_5=1$ . Use a Gram-Schmidt process to orthonormalize the coordinate basis vector on the original 2D projection to describe a 3D manipulation space, $\textbf{M}$.

@@

<!-- What the manip space facilitates -->
The manip space provides a 3D projection from $p$-dimensional space, where the coefficient of the manip var can range completely between [-1, 1]. 3D rotation can be used to rotate the mani variable completely into or completely out of a 2D projection. Figure \ref{fig:step2} illustrates this 3D manipulation space with the manip var highlighted. This representation is produced by calling the \code{view\_manip\_space()} function. Functionally, the manipulation space is more of a mathematical construct that needn't be visualized but this diagram provides intuition for the technique.

@@

<!-- describe manip var path -->
For a radial tour fix the (horizontal) angle within the projection plane, $\theta$, and define a sequence for the (vertical) angle coming out of the projection plane, $\phi$, bringing the initial $XY$ contributions of the manip var to a maximum and then to zero before returning to the initial position. Alternatively, for an oblique manual tour, capture the user manipulation directly on the $XY$ of the projection plane.

@@

<!--  phi transform and animation -->
The steps outlined above can be used to create any arbitrary rotation in the manip space. To use these for sensitivity analysis, the radial rotation is built into an animation where the manip var is rotated fully into the projection, completely out, and then back to the start. This involves changing $\phi$, the angle relative to its initial value. Apply the transformation $\phi_i \leftarrow \phi_i-\phi_1$. When $\phi$ is 0, the manip var is completely in the projection, and when $\phi$ is $\pi/2$, $\textbf{B}_k$ is not contributing at all.

@@

In each of the steps 3-5, a small step may be made to bring it exactly to the end position.

@@

```{r step4, echo=F, warning=F, fig.height=7.0, fig.width=5.83, out.height='7in', out.width='5.83in',                                                                fig.cap = "Radial manual tour manipulating aede2 of standardized flea data.  The contributions increase from its initial contribution to a full contribution to the projection before decreasing to zero and then returning to its initial value. Manipulating the coefficeients of aede2 changes the distance separating the purple cluster. This shows that aede2 is important for distinguishing this species from the ramaining data. Animated versions made with the \\code{play\\_manual\\_tour()} function and can be viewed at https://nspyrison.netlify.com/thesis/flea\\_manualtour\\_mvar5/."}
#play_manual_tour(f_dat, f_bas, f_mvar, col = f_cat, angle = f_angle)
array2static(.m_tour = f_mtour, .data = f_dat, .m_var = f_mvar, .cat = f_cat)
```

@@

The value of $\phi$ is relative to its initial value. The transformation $\phi_i$ - $\phi_1$ is useful to think about $\phi$ relative to the basis plane. Additionally, the value of $\phi$ may be out of phase by a factor of $\pi$. If the manip variable doesn't move as expected these are the first places to check.

## Data in projection-space {#sec:display}

@@

<!-- step 0 disp code. -->
```{r installCODEEXAMPLE, eval=F, echo=T}
# remotes::install_github("nspyrison/spinifex") # Development version
install.package("spinifex")
library("spinifex")

@@

<!-- summary of application  -->
Radial manual tours were applied to a dataset across different experiments of hadronic collisions. The importance of selecting the correct manip var, as demonstrated by comparing tours of varying amounts of structural information. Manual tours, by giving the full contribution of the manipulation space to the manip var, enable analysts to explore the sensitivity of the structure with the selected variable. This information can be used by domain experts to identify which variables are probing which parameter spaces and how sensitive those variables are to structural features. This insight can be indispensable for variable inclusion/exclusions in a model, or in high-level decisions, such as budgeting time and funding.

>>>>

- $\textbf{X}$, the data, an $n \times p$ numeric matrix to be projected to 2D.
- $\textbf{B} = (B_1,~ B_2)$, any 2D orthonormal projection basis, $p \times 2$ matrix, describing the projection from $p$ to two dimensions. We will call this the "original projection" because it is the starting point for the manual tour.
- $k$, is the index of the variable to manipulate, called the "manip var".
- $|\textbf{B}_k|$, the norm of the manip var, $k$, the length of this basis vector between 0 and 1 inclusive.
- $\textbf{e}$, a 1D coordinate zero basis vector of length $p$ with the $k$-th element set to one.
- $\textbf{M} = orthonormalize(\textbf{B}|\textbf{e})$, the manipulation space, a $p \times 3$ matrix where out-of-plane rotation takes place. 
- $\theta$, the angle of in-projection-plane rotation, for example, on the reference axes; $c_\theta, s_\theta$ are the cosine and sine.
- $\phi$, the angle of out-of-projection-plane rotation, into the manipulation space; $c_\phi, s_\phi$ are the cosine and sine.
- $\textbf{U}$, the axis of rotation for $\phi$.
- $\textbf{R}$, the rotation matrix, containing the rotaions of $\theta$ and $\phi$ within the manipulation space, $\textbf{M}$.
- $\textbf{RM} = \textbf{M} * \textbf{R}$, the result of the manipulation space after the application of the rotation matrix.
- $\textbf{P} = \textbf{X} * \textbf{RM}$, the data projection, the data as projected through the rotated manipulation space.

<!-- operate on bases -->
The algorithm operates entirely on projection bases and utilizes the data only later when making a display.

@@

<!-- Projection basis -->
An initial 2D projection basis set must be provided. One way to identify a projection containing interesting features is to apply a guided tour. In a guided tour, the projection sequence is selected by optimizing an index function via hill-climbing on the projection space. In this case, the holes index is selected and applied to the standardized flea data. The holes index is maximized when the projected observations are furthest from the center.

Figure \ref{fig:step0} shows a locally optimized projection of the data. The left panel displays the reference axes of the projection basis, a visual indication of the magnitude and direction each variable contributes to the projection. The right panel shows the data as projected through the basis set described by the reference axes (left). Data points are colored and given shape according to the species. Call \code{view\_basis()} on a basis to produce a \CRANpkg{ggplot2} [@wickham_ggplot2:_2016] object similar to Figure \ref{fig:step0}. The projected data is processed for display using matrix multiplication, $\textbf{P}_{[n,~d]} ~=~ \textbf{X}_{[n,~p]} ~*~ \textbf{B}_{[p,~d]}$.

@@

<!-- Zero Vect, manip sp -->
Initialize the coordinate basis vector as a zero vector $\textbf{e}$ of length $p$, and set the $k$-th element to 1. In the example data, aede2 is the fifth variable in the data, so $k=5$, set $e_5=1$. Use a Gram-Schmidt process to orthonormalize the coordinate basis vector on the original 2D projection to describe a 3D manipulation space, $\textbf{M}$.

@@

<!-- What the manip space provides -->
The manip space provides a 3D projection from $p$-dimensional space, where the coefficient of the manip var can range completely between [-1, 1]. 3D rotation can be used to rotate the manip variable completely into or completely out of a 2D projection. Figure \ref{fig:step2} illustrates this 3D manipulation space with the manip var highlighted. This representation is produced by calling the \code{view\_manip\_space()} function. Functionally, the manipulation space adds another layer of complexity that needn't be displayed in the final animation, but this diagram aids in comprehension of the technique.

@@

<!-- describe manip var path -->
For a radial tour fix the (horizontal) angle within the projection plane, $\theta$, and define a sequence for the (vertical) angle coming out of the projection plane, $\phi$, bringing the initial value of $|\textbf{B}_k|$ to a maximum and then to zero before returning to the initial position. Alternatively, for an *oblique* manual tour, capture the user manipulation directly on the $XY$ of the projection plane.

@@

<!--  phi transform and animation -->
The steps outlined above can be used to create any arbitrary rotation in the manip space. To use these for sensitivity analysis, the radial rotation is built into an animation where the manip var is rotated fully into the projection, completely out, and then back to the initial value. This involves changing $\phi$, the angle relative to its initial value. Apply the transformation $\phi_i \leftarrow \phi_i-\phi_1$ such that $\phi$ is relative to the projection plane. When $\phi$ is 0, $|\textbf{B}_k| = 1$, and when $\phi$ is $\pi/2$, the manip var has no contribution to the projection.

@@

In each of the steps 3-5, a small step may be appended to bring $\phi$ exactly to the desired value.

@@

```{r step4, echo=F, warning=F, fig.height=7.0, fig.width=5.83, out.height='7in', out.width='5.83in',                                                                fig.cap = "Radial manual tour manipulating aede2 of standardized flea data. The contributions increase from its initial vlaue to a full contribution to the projection before decreasing to zero and then returning to the initial value. Manipulating the coefficeients of aede2 changes the distance separating the purple cluster. This shows that aede2 is important for distinguishing this species from the ramaining data. Animated versions made with the \\code{play\\_manual\\_tour()} function and can be viewed at https://nspyrison.netlify.com/thesis/flea\\_manualtour\\_mvar5/."}
#play_manual_tour(f_dat, f_bas, f_mvar, col = f_cat, angle = f_angle)
array2static(.m_tour = f_mtour, .data = f_dat, .m_var = f_mvar, .cat = f_cat)
```

@@

The value of $\phi$ is relative to its initial value. The transformation $\phi_i$ - $\phi_1$ is useful to think about $\phi$ relative to the basis plane. Additionally, the value of $\phi$ may be out of phase by a factor of $\pi$. If the rotation does not behave as expected these are the first places to check.

## Projecting the data {#sec:display}

@@

```{r installCODEEXAMPLE, eval=F, echo=T}
# remotes::install_github("nspyrison/spinifex") # Development version
install.package("spinifex")
library("spinifex")

@@

<!-- summary of application  -->
Radial manual tours were applied to a dataset across different experiments of hadronic collisions. The importance of selecting the correct manip var, as demonstrated by comparing tours of varying amounts of structural information. Manual tours, by controlling the contribution of the manip var on the projection, enable analysts to explore the sensitivity that variable has on the structure of the projection. This information can be used by domain experts to identify which variables are probing which parameter spaces and how sensitive structural features are to different variables. This insight can be indispensable for variable inclusion/exclusion, and in higher-level decisions, such as meta-analysis, to suggest directions of future research.
